%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume-openfont}
\usepackage{fancyhdr}


\fancyfoot{}
\pagestyle{fancy}
\fancyhf{}



 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mihir}{Wadekar}{ \urlstyle{same}\href{http://mw2000.github.io}{mw2000.github.io}\\
\href{mailto:mpwadekar@ucdavis.edu}{mpwadekar@ucdavis.edu} | 408.647.0270 | \href{mailto:mwadekar2000@gmail.com}{mwadekar2000@gmail.com}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of \\ California, Davis}
\descript{BS in Computer Science}
\location{June 2022 | Davis, CA}
College of Engineering | College of \\ Letters and Science \\
\location{ \bf{GPA:} 3.69 / 4.0 \\}
\location{\bf{Dean's Honors List:} \\ Winter 2019 \textbullet{} Spring 2019 \\ \textbullet{} Fall 2019 \textbullet{} Spring 2020}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/mw2000}{\bf mw2000} \\
LinkedIn://  \href{https://www.linkedin.com/in/mihirwadekar/}{\bf mihirwadekar} \\
Twitter://  \href{https://twitter.com/that\_one\_nerdy\_}{\bf @that\_one\_nerdy\_} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Software Development and OOP \\
Data Structures and Algorithms \\
Operating Systems \\
Artificial Intelligence \\
Computer Security \\
Computer Architecture \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Over 5000 lines:}
C++ \textbullet{}  Python \textbullet{} Javascript \textbullet{} HTML5 \\
\location{Familiar:}
Solidity \textbullet{} Rust \textbullet{} x86 Assembly \textbullet{} Go\\

\vspace{5mm} %5mm vertical space

\subsection{Frameworks}
NodeJS \textbullet{} React Native \textbullet{} Arduino \textbullet{} \\ VueJS \textbullet{} Firebase
\sectionsep


\section{Student Orgs}
\runsubsection{\href{https://blockchainatdavis.io}{Blockchain At \\Davis}}
\descript{| President}
\vspace{5mm}
\runsubsection{\href{https://spaceandsatellitesystems.com}{Space and Satellite\\ Systems}}
\descript{| Software Lead}
\vspace{5mm}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{\href{https://mwadekar2000.wixsite.com/plasticoin/}{PlastiCoin}}
\descript{| Co-Founder }
\location{Oct 2018 - Apr 2020 | Davis, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Started a blockchain startup to incentivize waste recycling.
\item Managed a team of 5+ people.
\item Built an application and an ERC20 token, using React Native and Solidity respectively.
\end{tightemize}
\sectionsep

\runsubsection{\href{http://cateno.io/}{Cateno: ICO Governance Platform}}
\descript{| Founding Engineer }
\location{July 2019 – Nov 2019 | San Francisco, CA}
\begin{tightemize}
\item Helped take key startup decisions.
\item Built front end using VueJS and used Firebase for user authentication. 
\item Used web3 to connect exisiting smart contracts with the front end.
\end{tightemize}
\sectionsep

\runsubsection{\href{http://www.flairminds.com/}{Flair Minds Software Solutions}}
\descript{| Front-End Intern }
\location{Aug 2019 – Sep 2019 | Pune, India}
\begin{tightemize}
\item Designed web applications with Material UI.
\item Used Angular 8 to write services and connect to an SQL database.
\item Developed software using the SCRUM methodology.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{\href{https://expolab.org/}{Expo Lab}}
\descript{| Undergraduate Researcher}
\location{Feb 2019 – June 2019 | Davis, CA}
Researched real-world applications of blockchain in sustainability and waste management under Dr. Mohammed Sadoghi.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

%\runsubsection{\href{https://github.com/uc-davis-space-and-satellite-systems/efos}{Flight Operating System}}
%\descript{}
%\begin{tightemize}
%\item Developed as a part of the Space and Satellite Subsystems CS/Software team.
%\item Enables autonomous determination, control, operation, and communications of the UC Davis 'Spaceblock' CubeSAT.
%\item Made using Python3.
%\end{tightemize}
%\sectionsep

\runsubsection{\href{https://github.com/mw2000/DAG/}{Decentralized Autonomous Governance}}
\descript{}
\begin{tightemize}
\item A governance platform based on allowing people to make their own propositions, vote on them  and govern themselves.
\item Used solidity to make the collection of smart contracts on an Ethereum testnet, comprising the platform.
\item Can be applied to university student governments.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/mw2000/Injecto}{Injecto}}
\descript{}
\begin{tightemize}
\item A governance platform based on allowing people to make their own propositions, vote on them  and govern themselves.
\item Used solidity to make the collection of smart contracts on an Ethereum testnet, comprising the platform.
\item Can be applied to university student governments.
\end{tightemize}
\sectionsep

\sectionsep


\section{Teaching}
\runsubsection{ECS 189F - Databases}
\descript{}
Developed curriculum for an open source blockchain class to be taught at UC Davis in Fall 2020, along with Blockchain at Davis, Blockchain Acceleration Foundation and Dr. Mohammad Sadoghi.
\sectionsep
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
